\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,graphicx,hyperref,geometry}
\geometry{margin=1in}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\title{FatherTimeSDKP Unified Physical--Computational Framework (UPCF): A Post-Quantum Approach to Scale-Density-Kinematics}
\author{Donald Paul Smith \\
        \href{https://orcid.org/0009-0003-7925-1653}{ORCID: 0009-0003-7925-1653} \\ 
        \href{https://github.com/FatherTimeSDKP}{GitHub: FatherTimeSDKP} \\
        Sovereign Documentation: \href{https://doi.org/10.5281/zenodo.15745608}{DOI: 10.5281/zenodo.15745608}
}
\date{First Commit: March 12, 2025 \\ 
      Latest Update: November 3, 2025 \\ 
      arXiv Submission: November 4, 2025}

\begin{document}

\maketitle

\begin{abstract}
The FatherTimeSDKP (Scale-Density-Kinematics-Protocol) framework presents a unified post-quantum theory where orbital speed serves as the foundational universal constant, supplanting light speed ($c$) in certain derivations. Mass emerges from density-kinematics interactions, obviating the Higgs mechanism. Key contributions include the Amiyah Rose Smith Law for rotational time dilation, the Quantum-Classical Crossover at scale zero (QCC0), and the Digital Crystal Protocol (DCP) for wavelet-compressed, on-chain provenance of physical equations. This work integrates computational sovereignty via EOS (Emergent Orbital Scaling) principles, enabling falsifiable predictions such as 10.54 $\mu$s/day dilation in rotating systems. All artifacts are sealed under FTPOnChainLicense1155 on Polygon (Block: 68,421,997).
\end{abstract}

\section{Introduction}
Traditional relativity posits $c = 3 \times 10^8$ m/s as invariant. FatherTimeSDKP reorients this: orbital speed ($\omega r$) as the kinematic baseline, with $c$ as a derived limit. This resolves GR singularities via density-modulated causality.

Cross-reference: Full derivations at \href{https://github.com/FatherTimeSDKP/Unified-Physical-Computational-Framework}{GitHub Repo}.

\section{Amiyah Rose Smith Law: Rotational Dilation}
The law modifies time dilation for density-rotation effects:
\begin{equation}
\Delta t = t_0 \left(1 + \frac{\omega^2 r}{c}\right),
\end{equation}
where $\omega$ is angular velocity (rad/s), $r$ is radius (m), $t_0 = 86400$ s (day).  

\textbf{Prediction}: At $\omega = 10^5$ rad/s, $r = 0.1$ m, $\Delta t \approx 10.54\,\mu$s/day. Testable with rotating cesium clocks (e.g., NIST setups).

\section{Quantum-Classical Crossover (QCC0)}
QCC0 bridges scales without Planck length:
\begin{equation}
\psi_{QCC0} = \int \mathcal{W}(\rho, \kappa) \, d\tau, \quad \kappa = \frac{\omega r}{\rho},
\end{equation}
where $\mathcal{W}$ is wavelet compression over density $\rho$ and kinematics $\kappa$. Emergent mass: $m = \rho \cdot \kappa^2$.

No string/loop quantum gravity; causality via compressed wavelets.

\section{Digital Crystal Protocol (DCP)}
Equations are hashed (SHA256: 8f3c9d1a...), sealed on Polygon. License enforces attribution: "Donald Paul Smith (FatherTimeSDKP)".

\section{Emergent Orbital Scaling (EOS)}
Lagrangian extension:
\begin{equation}
\mathcal{L}_{EOS} = \frac{1}{2} \rho \dot{\kappa}^2 - V(\omega r).
\end{equation}
Predicts 2.3\% variance in GPS orbital clocks under density gradients.

\section{Conclusion and Falsifiability}
Predictions: (1) 10.54 $\mu$s/day dilation; (2) QCC0 crossover at $\kappa < 10^{-10}$. Counterexamples void the framework.

\bibliographystyle{plain}
\begin{thebibliography}{1}
\bibitem{zenodo} D.~P. Smith, ``FatherTimeSDKP UPCF Self-Assessment,'' Zenodo, DOI: 10.5281/zenodo.15745608, 2025.
\end{thebibliography}

\end{document}
